---
title: "ETF flows"
output: html_notebook
---

```{r initialize}
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
```


```{r import}
ACIM <- read_excel("etf_navs/ACIM.xls", skip = 3)
ACIM
```
There are several lines at the bottom for the disclaimers and legal information, we will remove those, and then format the columns into the correct type, date and numeric.

```{r}
ACIM <- ACIM %>% 
  select(1:4) %>% 
  filter(!is.na(Nav)) %>% 
  mutate(Date = dmy(Date)) %>% 
  modify_at(2:4, as.numeric)
```

Now the dataframe would rank correctly by date

```{r}
ACIM %>%
  top_n(-5, Date)
```

Now we will try to produce a function that imports and cleans all the SPDR etf xls files and combine them. First get all the tickers from the xls and use that retrieve the files.

```{r get_spdr_tickers}
spdr_tickers <- read_excel('spdr_etfPerformance.xls', range = cell_cols("B")) %>% 
  filter(!is.na(TICKER)) 
  
spdr_tickers
```

Nowe we have tickers, write a function that will read the excel into the dataframe.

```{r import_function}
importclean <- function(ticker) {
  #combine ticker and location string to create location
  location <- str_interp("etf_navs/${ticker}.xls")
  
  #uses the location to read the excel file in the folder
  xls_file <- read_excel(location,skip = 3)
  
  #cleans the data, removes the disclaimers at the end and converts to numeric
  xls_file <- xls_file %>% 
    select(1:4) %>% 
    filter(!is.na(Nav)) %>% 
    mutate(Date = dmy(Date)) %>% 
    modify_at(2:4, as.numeric)
  
  return(xls_file)
}
```

Test the function out real quick

```{r test}
test = importclean('ACIM')
test
```

works perfectly

```{r import_all}
spdr_history <- spdr_tickers %>%
  pull(TICKER) %>% 
  map(~importclean(.x))
```

```{r}
spdr_total <- add_column(spdr_tickers, history = spdr_history) %>% 
  unnest(history)
```

```{r}
spdr_total %>% 
  filter(TICKER=='ACIM') %>%
  top_n(5, Date)
```

```{r import_function}
importholdingclean <- function(ticker) {
  #combine ticker and location string to create location
  location <- str_interp("etf_navs/${ticker}.xls")
  
  #uses the location to read the excel file in the folder
  xls_file <- read_excel(location,skip = 3)
  
  #cleans the data, removes the disclaimers at the end and converts to numeric
  xls_file <- xls_file %>% 
    select(1:4) %>% 
    filter(!is.na(Nav)) %>% 
    mutate(Date = dmy(Date)) %>% 
    modify_at(2:4, as.numeric)
  
  return(xls_file)
}
```

