---
title: "Holdings and price information"
output: html_notebook
---

```{r initialize, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
library(feather)
```

Let's take a look at the holdings data.

```{r}
hs <- read_feather('data/clean/combined_holdings.feather')
hs
```

let's take a look at the stocks in the etfs

```{r}
hs %>% 
  group_by(id) %>% 
  select(2:3) %>% 
  count(id) %>% 
  arrange(desc(n))
```

So there are a total of 10,623 entries, but there are quite a bunch of them that are not stocks. For example the top few here are treasury/cash.


```{r}
stocks <- hs %>% 
  select(id) %>% 
  distinct()
stocks
```

```{r}
stocks %>% 
  filter(str_detect(id, "[\\d-]+")==TRUE)
```

6,411 of them are foreign stocks, so let's remove those

```{r}
fs <- stocks %>% 
  filter(str_detect(id, '[\\d-]+')!=TRUE) %>% 
  pull(id)
fs[1:5]
```

let's see what these symbols are to make sure they are stocks

```{r}
hs %>% 
  filter(id%in%fs) %>% 
  group_by(id) %>% 
  count(name) %>% 
  group_by(id) %>% 
  count(id) %>% 
  filter(nn>1) %>% 
  arrange(desc(nn))
```

```{r}
hs_filtered <- hs %>% 
  filter(id%in%fs)
```

There are a few etfs that have duplicate stock entries in them, we have to clean those

```{r}
hs_filtered %>% 
  group_by(ticker, id) %>% 
  summarise(n=n()) %>% 
  filter(n==2) %>% 
  arrange(desc(n))
```

mainly, MDY got imported twice so we need to fix these

```{r}
hs_filtered <- hs_filtered %>% filter(ticker!='MDY') %>% bind_rows(mdy)
hs_filtered
```

then replace the names so they are all the same

```{r}
hs_filtered <- hs_filtered %>% 
  group_by(id) %>% 
  mutate(name=(name[1]))
```

save this data real quick

```{r}
write_feather(hs_filtered, 'data/clean/us_holdings.feather')
```

