---
title: "Nav/holding integration"
output: html_notebook
---

```{r initialize, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
library(feather)
library(knitr)
```

##Holdings

Lets integrate the holdings by ticker first

```{r}
ishare.holdings <- read_feather("data/clean/ishare_holdings.feather")
spdr.holdings <- read_feather("data/clean/spdr_equity_holding.feather")
```

reduce the variables in the ishares data and rearrange/rename it to match with the spdr data

```{r}
ish.matched <- ishare.holdings %>% 
  select(c(1,3,2,5,7,10)) %>% 
  rename(weight = 'Weight_(%)')

colnames(ish.matched) <- str_to_lower(colnames(ish.matched))
ish.matched
```

now rearrange the spdr data, and rearrange/rename it also

```{r}
spdr.matched <- spdr.holdings %>% 
  select(c(1,2,3,4,6,5)) %>% 
  rename(shares='Shares_held') %>% 
  rename(id='Identifier')

colnames(spdr.matched) <- str_to_lower(colnames(spdr.matched))
spdr.matched
```

now bind them on top of each other

```{r}
combined.holdings <- bind_rows(ish.matched, spdr.matched)

combined.holdings
```

```{r}
write_feather(combined.holdings, "combined_holdings.feather")
```

time to take a look at the data

```{r}
combined.holdings %>% 
  group_by(sector) %>% 
  count() %>% 
  arrange(desc(n))
```

Seems like there is a lot of consumer descretionary and financials

```{r}
combined.holdings %>% 
  group_by(name) %>% 
  count() %>% 
  arrange(desc(n))
```

top few holdings are the treasury and cash fund of course, followed up some conglomerates.

##NAV history

Time to integrate the NAV histories together

```{r}
ish.nav <- read_feather('data/clean/ishare_nav.feather')
sp.nav <- read_feather('data/clean/spdr_nav.feather')
```

```{r}
tibble(colnames(ish.nav))
```

```{r}
tibble(colnames(sp.nav))
```

lets mutate ishares data into total net assets, and then fix up the column names

```{r}
ish.m <- ish.nav %>% 
  mutate(total = NAV_per_Share*Shares_Outstanding) %>% 
  select(c(1,2,4,5,6))
ish.m
```

```{r}
sp.m <- sp.nav %>% 
  rename(shares = `Shares Outstanding`) %>% 
  rename(total = `Total Net Assets`)

colnames(sp.m) <- str_to_lower(colnames(sp.m))
sp.m
```

```{r}
colnames(ish.m) <- colnames(sp.m)
combined_nav <- bind_rows(ish.m, sp.m)
combined_nav
```


```{r}
created <- combined_nav %>% 
  group_by(ticker) %>% 
  summarise(date = min(date))

created$date <- created$date - days(1)

created <- created %>% mutate(nav=0, shares=0, total=0)

combined_nav <- bind_rows(combined_nav, created)
```

```{r}
write_feather(combined_nav, "data/clean/combined_nav.feather")
```






