---
title: "SPDR_holdings_import"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r initialize, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)
```

Now we will import the holdings information

first lets take a look at the file structure

```{r}
ACIM_holdings <- read_excel("etf_navs/ACIM_holdings.xls", skip = 3)
ACIM_holdings
```

Same as before we need to clean for disclaimers and type conversions

```{r}
ACIM_holdings %>% 
  filter(!is.na(Weight)) %>% 
  modify_at(c(3,5), as.numeric)
```

Nice and tidy. Create the ticker index as before.

```{r get_spdr_tickers}
spdr_tickers <- read_excel('raws/spdr_etfPerformance.xls', range = cell_cols("B")) %>% 
  filter(!is.na(TICKER)) 
  
spdr_tickers
```

The function to import the holdings information, modified from before. It needs to be modified for the fixed income holdings though, they have different formats

```{r}
SPAB_holdings <- read_excel("etf_navs/SPAB_holdings.xls", skip = 3)
SPAB_holdings
```


```{r}
colnames(SPAB_holdings)
str_detect(colnames(SPAB_holdings), 'Coupon') %>% 
  sum()

```


```{r import_holding_function}
importholdingclean <- function(ticker) {
  #combine ticker and location string to create location
  location <- str_interp("etf_navs/${ticker}_holdings.xls")
  
  print(str_c('Trying to import.....', ticker))
  #uses the location to read the excel file in the folder
  xls_file <- read_excel(location,skip = 3)
  
  #cleans the data, removes the disclaimers at the end and converts to numeric
  #checks first if the xls is for a bond ETF, print and move to next if it is.
  if (sum(str_detect(colnames(xls_file), 'Coupon')) > 0) {
    print(str_c(ticker, ' exception: is a bond ETF'))
  } else if (length(colnames(xls_file)) != 5) {
    print(str_c(ticker, ' exception: unexpected width'))
  } else {
    xls_file <- xls_file %>% 
      filter(!is.na(Weight)) %>% 
      modify_at(c(3,5), as.numeric) %>% 
      rename(Shares_held = 'Shares Held')

    return(xls_file)
  }
}
```

see if it works

```{r}
importholdingclean('SPAB')
```
works fine

this does not work for bond holdings though, because there are a different # of columns and format

apply same logic as nav_history

```{r import_all_holdings, message=FALSE, warning=FALSE, include=FALSE}
spdr_holdings <- spdr_tickers %>%
  pull(TICKER) %>% 
  map(~importholdingclean(.x))
```

didn't crash this time

```{r}
spdr_total_holdings <- add_column(spdr_tickers, holdings = spdr_holdings)
```

put the two together and select only the equity etfs

```{r}
spdr_equity_holdings <- spdr_total_holdings %>% 
  filter(str_detect(holdings, 'exception') == FALSE)
```

then unnest
```{r}
spdr_equity_holdings <- spdr_equity_holdings %>% 
  unnest(holdings)
```

save it to a feather and we are done

```{r}
library(feather)
write_feather(spdr_equity_holdings, "spdr_equity_holding.feather")

```

